Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-11 Grassmannian_cells.tex
improved proof of Lemma 4.4, minor changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

@@

Fix a natural number $n\geq 3$ and consider the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
For $m=1$, we assume that $\dim(\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=\alpha_1,\ldots,\alpha_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
Recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, sinks become sources and vice versa.
For $m\geq 2$, we build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates, i.e. we have
\begin{align}
  \label{recursive}
  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
\end{align}
It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.

@@

As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}. Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$. Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)}),\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
----TO HERE----DO NOT NEED THIS----
\end{comment}

\begin{lemma}
  \label{AR}
  \footnote{special case $m=3$}
  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Do parts (2), (3), (4) have analogues for $K(n)$?  The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.  The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}\sayT{The sequence (6) should have an analogue on $K(n)$. I would be happy with a direct proof of (1) and (2). I did not check the details so far.
	(4) and the first half of (3) hold only on the universal cover. We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
  Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
  Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
  $$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$

  The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \begin{align}
        \label{ses3}
        \sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}
      \end{align}
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.

    %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
  \end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$. Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively. We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section. Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.

In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$. In order to deduce the statement from (\ref{recursive}) for general $m$, it remains to show the statement for $m=5$. Therefore, we consider the short exact sequence
\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
and apply the reflection functor $\tilde\Sigma_2$ twice which is the same as applying $\tau^{-1}$. As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, the statement follows for $m=5$ and thus for general $m$.

Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
$$\ses{P(3,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
Actually, the first summand of $P(3,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left. This shows the second statement.

@@

\end{proof}
Define 
$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$

If $m=3$, we replace the short exact sequence (\ref{ses3}) by
 \begin{align}
   \label{ses4}
   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)\ar[r] & 0}.
 \end{align}
 Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{a_{j_l}}(1,a_{j_l})\right)$, see also Example \ref{smallm}.

@@

For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$. We define the admissible sequence $\delta {\bf j}$ by
\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\kk$. Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
		for $k=1,\ldots,r$.
  \end{enumerate}
\end{lemma}
\begin{proof}

@@

The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$. We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$. We use the third statement in order to successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]

@@

\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
Using Lemma \ref{le:properties}.(3), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
	\end{proof}
The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars. Let $\uj=(j_{1},\ldots,j_{l})\in I_l$. It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$. We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$. We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$. Therefore, we need to apply a translated version of this morphism. In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.

Our construction immediately yields the following lemma.
\begin{lemma}\label{projections}
Let $\tilde P_m$ be a lift of the preprojective representation $P_m$ and let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
\[\pi_m^{\bf j}=\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}\circ\ldots\circ\pi^{\underline{j_2}}_{m-1,j_1^c}\circ\pi_m^{\underline{j_1}}.\]
Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
\[\pi_{m-k+1,j_{k-1}^c}^{\underline{j_k}}=\prod_{i=1}^{n-2} \pi^{j_{k,l_{i}}}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,j_{r-1}^c}^{\underline{j_r}}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
\end{lemma}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}\label{sec:RepK(n)}

@@

Fix a natural number $n\geq 3$ and consider the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$.
For $m=1$, we assume that $\dim(\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$.
Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=\alpha_1,\ldots,\alpha_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
Recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, sinks become sources and vice versa.
For $m\geq 2$, we build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates, i.e. we have
\begin{align}
  \label{recursive}
  \tilde P_m=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
\end{align}

It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.

@@

As the sequence does not split, this shows that $U'$ is an indecomposable preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$ where the indecomposability follows from \cite[Lemma 3.12]{wei2}. Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$. Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l}}< 0$, we obtain
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

@@

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(i_1,\ldots,i_{n-1})}\cong\tilde P_{m-1}^{(i_n)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)}),\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.\footnote{do we need this? See also proof of Lemma 4.5}
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows for instance by induction when applying BGP-reflections.
\end{proof}
----TO HERE----DO NOT NEED THIS----
\end{comment}
Define 
$$P(m,\uj):=\begin{cases}\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}\text{ if }m\geq 4\\\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{1,(j_l,i)}\text{ if }m=3\end{cases}$$

\begin{lemma}
  \label{AR}
  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Do parts (2), (3), (4) have analogues for $K(n)$?  The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.  The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}\sayT{The sequence (6) should have an analogue on $K(n)$. I would be happy with a direct proof of (1) and (2). I did not check the details so far.
	(4) and the first half of (3) hold only on the universal cover. We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
  Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
  Consider the short exact sequence $$\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}.$$ The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \begin{align}
        \label{ses3}
        \ses{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}%{\pi^{\bf j_l}_{m-1}}
      \end{align}
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.

    %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
  \end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Using the identities (\ref{recursive}), it suffices to prove all statements for $m=4$ and arbitrary $1\leq l\leq n-1$. Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively. We should point out that it is very important for this proof that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section. Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.

In Example \ref{smallm} it was shown that $\tau \tilde P_4^{(1,\ldots,l)}=\tilde P_2^{(1,\ldots,l)}$. For $m=5$,  we consider the short exact sequence
\[\ses{\bigoplus_{i=1}^l\tilde P_{2,i}}{\tilde P_3}{\tilde P_3^{(1,\ldots,l)}}\]
and apply the reflection functor $\tilde\Sigma_1\tilde\Sigma_2$ which is the same as applying $\tau^{-1}$. As we have $\tau^{-1} \tilde P_{2,i}=\tilde P_{4,i}$ and $\tau^{-1}\tilde P_3=\tilde P_5$, it follows that $\tau^{-1}\tilde P_3^{(1,\ldots,l)}=\tilde P_5^{(1,\ldots,l)}$ which is statement for $m=5$. The general statement follows from the identities (\ref{recursive}). Note that this also shows that
\[(\tilde \Sigma_2\tilde P_{m}^{(1,\ldots,l)})^\sigma=\tau^{-1}\tilde P^{(1,\ldots,l)}_{m-1}.\]

Considering the quiver $\tilde P_{3,l}$ from Example \ref{smallm}, it is clear that we obtain an exact sequence
$$\ses{P(4,(1,\ldots,l))}{P_{3,l}}{\tilde P_2^{(1,\ldots,l)}}.$$
Actually, the first summand of $P(4,(1,\ldots,l))$ corresponds to the quivers $\tilde A_i$ at the bottom and the second summand to the $l-1$ sources in the second row lying on the left. Together with the first statement and the identities (\ref{recursive}), this shows the second statement.

@@

If $m=3$, we replace the short exact sequence (\ref{ses3}) by
 \begin{align}
   \label{ses4}
   \xymatrix{0\ar[r] &P(3,\uj)\ar[r] &  \tilde P_{2,j_l}\ar[r] & \left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)\ar[r] & 0}.
 \end{align}
 Recall that the image of the unique homomorphism $\tilde P_{2,j_l}\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is just $\tau'\tilde P_3^{\uj}:=\left((2,1)\xrightarrow{\alpha_{j_l}}(1,\alpha_{j_l})\right)$, see also Example \ref{smallm}.

@@

%For $\uj\in I_{l}$ with $l\leq n-1$, there exist unique short exact sequences 
%\[\ses{\bigoplus_{i=1}^l\tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}},\quad\quad\ses{\tilde P_{m-1,j_l}}{\tilde P_{m}^{(j_1,\ldots,j_{l-1})}}{\tilde P_{m}^{\uj}}.\]
The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf j}=(\underline{j_1},\underline{j_2},\ldots,\underline{j_r})$. We define the admissible sequence $\delta {\bf j}$ by
\[\delta {\bf j}:=((j_1^c,\underline{j_2}),\underline{j_3},\ldots,\underline{j_r}).\]
We recursively define $\delta^i{\bf j}$ for $i=1,\dots,r$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\uj=(j^c)$ for $\uj\in I_{n-1}$. We obtain the following analogue of Lemma \ref{cor:truncated preprojective isomorphism}.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item If $\uj\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\uj}\cong \tilde P_{m-1,j^c}^{\uj^c}= \tilde P_{m-1,j^c}/\tilde P_{m-2,(j^c,j^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf j:=(\underline{j_1},\ldots,\underline{j_r})$ be an admissible sequence. The truncated preprojective representation
		$$\tilde P^{\mathbf j}_{m-r+1}:=\tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{(j_{r-1}^c,j_{r,1},\ldots,j_{r,s})}$$
	 is a quotient of $\tilde P_m$ such that $\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})=\CC$. Defining ${\bf j}(k):=(\underline{j_1},\ldots,\underline{j_k})$ for $k=2,\ldots,r-1$, these quotients satisfy the relation
		\[\tilde P_{m-k,(j_1^c,\ldots,j_k^c)}^{\delta^k{\bf j(k)}}=\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}\bf j(k)}\]
		for $k=1,\ldots,r$.
  \end{enumerate}
\end{lemma}
\begin{proof}

@@

The second statement is now obtained recursively when initially considering the commutative diagram from above replacing $\uj$ by $\underline{j_1}$. We have $\delta^{k-1}{\bf j}(k)=(j_{k-1}^c,j_{k,1},\ldots,j_{k,n-1})$ and $\delta^{k}{\bf j}(k)=(j_k^c)$. We successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{n-2}\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})}\ar[r] &  \tilde P^{(j_{k-1}^c)}_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}\ar[r] & \tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)}^{\delta^{k-1}{\bf j}(k)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(k+1),(j_1^c,\ldots,j_{k}^c,j_k^c)} \ar[r]\ar[u] & \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}\ar[u]\ar[r]& \tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)}\ar[r]\ar@{=}[u]& 0}\]

@@

\[\xymatrix{0\ar[r] &\bigoplus_{i=1}^{s}\tilde P_{m-r,(j_1^c,\ldots,j_{r-1}^c,j_{r,i})}\ar[r] &  \tilde P^{(j_{r-1}^c)}_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(j_1^c,\ldots,j_{r-1}^c)}^{{\bf j}}\ar[r] & 0 }.\]
Using Lemma \ref{le:properties}.(2), we recursively obtain	$\Hom(\tilde P_m,\tilde P^{\mathbf j}_{m-r+1})\cong\Hom(\tilde P_m,\tilde P_{m-k,(j_1^c,\ldots,j_{k}^c)}^{(j_{k}^c)})=\kk$.
%As $\Hom(\tilde P_{m-k,(j_1^c,\ldots,j_{k-1}^c,j_{k,i})},\tilde P_{m-k+1,(j_1^c,\ldots,j_{k-1}^c)})=\kk$ for all $k=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf j}$ is uniquely determined.
	\end{proof}
The lemma implies that there is a morphism by $\pi_m^{\bf j}:\tilde P_m\to \tilde P_{m-r+1}^{\bf j}$ which is unique up to scalars. Let $\underline{j_1}=(j_{1,1},\ldots,j_{1,n-1})$ and $\uj=(j_{1,1},\ldots,j_{1,l})\in I_l$. It is important for us that this morphism factors through the truncated preprojective $\tilde P_m^{\uj}$. We denote the quotient morphism from $\tilde P_m^{\uj}$ to $\tilde P_{m-r+1}^{\bf j}$ by $\pi_{m,\uj}^{\bf j}$. We want to apply $\pi_m^{\bf j}$ also to translated representations $w.\tilde P_m$, mostly for $w\in\{a_i,a_i^{-1}\}$. Therefore, we need to apply a translated version of this morphism. In abuse of notation, we also denote these morphisms by $\pi_m^{\bf j}$ and $\pi_{m,\uj}^{\bf j}$.

Our construction immediately yields the following lemma.
\begin{lemma}\label{projections}
Let ${\bf j}=(\underline{j_1},\ldots,\underline{j_r})$ with $r\leq m-1$ and $\underline{j_r}\in I_s$ be an admissible sequence with entries $j_{k,i}$ for $k=1,\ldots r$. Then we have
\[\pi_m^{\bf j}=\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}\circ\ldots\circ\pi^{(j_{2}^c,\underline{j_2})}_{m-1,(j_1^c)}\circ\pi_m^{\underline{j_1}}.\]
Moreover, for every sequence $(l_1,\ldots,l_{n-2})\in I_{n-2}$, we have
\[\pi_{m-k+1,(j_{k-1}^c)}^{(j_{k-1}^c,\underline{j_k})}=\prod_{i=1}^{n-2} \pi^{(j_{k-1}^c,j_{k,l_1},\ldots, j_{k,l_{i}})}_{m-k+1,(j_{k-1}^c,j_{k,l_1},\ldots,j_{k,l_{i-1}})}\]
for $k=2,\ldots,r-1$. The analogous statements hold for $\pi_m^{\underline{j_1}}$ and  $\pi_{m-r+1,(j_{r-1}^c)}^{(j_{r-1}^c,\underline{j_r})}$ when replacing $n-2$ by $n-1$ and $s-1$ respectively.
\end{lemma}
